\documentclass{article}
\usepackage[utf8]{inputenc}

\title{A Test of Open Book}
\author{Michal Hoftich}
\date{January 2020, updated June 2021}
\usepackage{hyperref}
\usepackage{listings}
\newcommand{\cmdname}[1]{\texttt{#1}}
\newcommand\footurl[1]{\footnote{\url{#1}}}
\newcommand\urllink[2]{#1\footurl{#2}}
\newcommand\foothref[3]{#1\footnote{\href{#2}{#3}}}
\usepackage{upquote}

\begin{document}

\maketitle

\section{Introduction}

This is a test of the Latex2html tool.

\section{Prompt}

What is prompt-learning?



\section{Setup}

\subsection{On Overleaf}

First step is to sync your Overleaf project with your GitHub account, following \foothref{a guide on 
  Overleaf}{https://www.overleaf.com/learn/how-to/How_do_I_connect_an_Overleaf_project_with_a_repo_on_GitHub,_GitLab_or_BitBucket\%3F}
{\texttt{https://www.overleaf.com/learn/how-to/How\_do\_I\_connect\_an\_Overleaf\_project\_with\_a\allowbreak\_repo\_on\_GitHub,\_GitLab\_or\_BitBucket\%3F}}. 
Don't forget to run the \cmdname{Sync -> GitHub} command from Overleaf main menu every time you had updated the document.

\subsection{On GitHub}
Next step is to configure actions in the Github project created for your
document. Two steps are necessary -- first  one compiles the document to HTML
using \TeX4ht, the second step publishes the generated HTML files on the Web
using \urllink{GitHub Pages}{https://pages.github.com/}

For the web publishing we  use the \verb|actions-gh-pages|
\urllink{action}{https://github.com/peaceiris/actions-gh-pages}. 

When the keys are set up, you can create the workflow file. Select the
\cmdname{Actions} tab and click the \cmdname{Set up a workflow yourself}
button. It will open an editor with a YAML file for the Action workflow.
Replace it with the following content:

% I am just testing if this command works in the container
\AtEndEnvironment{lstlisting}{\relax}

\begin{lstlisting}{yaml}
name: CI
on: [push]
jobs:
  build:
    runs-on: ubuntu-latest
    steps:
    - uses: actions/checkout@v1
    - name: Run make4ht
      uses: docker://ghcr.io/michal-h21/make4ht-action:latest
      env:
        command: "make4ht -u -d out main.tex"
    - name: Publish the web pages
      uses:  peaceiris/actions-gh-pages@v3
      with:
        github_token: ${{ secrets.GITHUB_TOKEN }}
        publish_dir: ./out
\end{lstlisting}

The important part of the configuration is the \cmdname{command} key. It
contains the actual command used for the compilation. We use
\urllink{Make4ht}{https://ctan.org/pkg/make4ht?lang=en}, build system for
\TeX4ht.

Command \verb|"make4ht -u -d out main.tex"| creates UTF-8 encoded HTML file
from the \cmdname{main.tex} input file. The \texttt{-d} option specifies the
output directory for the HTML files. This directory will be used for the web
publishing and should be passed to the \verb|publish_dir| key in
\textit{Publish the web pages} step.

The web will be published at \url{https://yourgitubusename.github.io/project_name/main.html}. 
\section{Links}
\begin{itemize}
    \item This document: \url{https://www.kodymirus.cz/overleaf-html-sample/main.html}
    \item Source repository: \url{https://github.com/michal-h21/overleaf-html-sample} 
\end{itemize}
 



\end{document}
